---
title: "Reality Capture"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Reality Capture}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>")
```

## Overview

The **Reality Capture API** lets you generate 3D models, point clouds, and orthophotos from photographs using photogrammetry. You provide a set of overlapping images of an object or scene, and APS processes them into a 3D model in your chosen output format.

Typical workflow:

1. **Authenticate** — get a 2-legged token.
2. **Create a photoscene** — define the output format.
3. **Upload images** — send your photographs to the photoscene.
4. **Process** — trigger photogrammetry processing.
5. **Poll for completion** — wait until the model is ready.
6. **Download** — retrieve the finished 3D model.

## Authentication

```{r eval=FALSE}
library(AutoDeskR)

tok <- getToken(
  id     = Sys.getenv("client_id"),
  secret = Sys.getenv("client_secret"),
  scope  = "data:read data:write data:create"
)
```

## Create a Photoscene

```{r eval=FALSE}
ps <- createPhotoscene(
  name   = "building-survey",
  format = "obj",
  token  = tok
)

photoscene_id <- ps$content$photoscene$photosceneid
```

Supported output formats:

| Format | Description |
|--------|-------------|
| `rcm`  | ReCap point cloud (default) |
| `rcs`  | ReCap scan |
| `obj`  | Wavefront OBJ mesh |
| `ortho`| Orthophoto |
| `report` | Quality report only |

## Upload Images

Provide a character vector of local file paths. The Reality Capture API supports JPEG and PNG images. For best results, use 20–300 overlapping photos with at least 60% overlap between adjacent shots.

```{r eval=FALSE}
image_files <- list.files("~/survey-photos", pattern = "\\.jpg$", full.names = TRUE)

imgs <- uploadImages(
  photoscene_id = photoscene_id,
  files         = image_files,
  token         = tok
)
```

## Start Processing

```{r eval=FALSE}
proc <- processPhotoscene(
  photoscene_id = photoscene_id,
  token         = tok
)
```

## Wait for Completion

Processing is asynchronous and can take several minutes to hours depending on the number of images. Use `waitForPhotoscene()` to block until it finishes:

```{r eval=FALSE}
done <- waitForPhotoscene(
  photoscene_id = photoscene_id,
  token         = tok,
  interval      = 30,    # poll every 30 seconds
  timeout       = 3600,  # give up after 1 hour
  verbose       = TRUE
)
```

Or poll manually with `checkPhotoscene()`:

```{r eval=FALSE}
status <- checkPhotoscene(photoscene_id = photoscene_id, token = tok)
status$content$photoscene$progress      # e.g. "75"
status$content$photoscene$progressmsg   # e.g. "Processing..."
```

## Download the Result

Once processing reaches 100%, download the output via the Model Derivative API. First get the output URN from the manifest, then download the file:

```{r eval=FALSE}
encoded_urn    <- jsonlite::base64_enc(photoscene_id)
manifest       <- getOutputUrn(urn = encoded_urn, token = tok)

encoded_output <- jsonlite::base64_enc(manifest$content$derivatives[[1]]$children[[1]]$urn)
result <- downloadFile(
  urn        = encoded_urn,
  output_urn = encoded_output,
  token      = tok,
  destfile   = "building-survey.obj"
)
```

## Tips

- Use images with consistent exposure and focus.
- Aerial (drone) images should have at least 80% overlap.
- The API supports up to 1,000 aerial or 300 hand-held images per photoscene.
- Processing time depends on the number of images and server load.
